The Name of the Title Is Hope

### 2024-11-26 paper/paper.tex
grammar

The synthesis framework is three-fold; namely, select-measure-generate\cite{McKenna2022}. We first select the important marginals to preserve, measure them by adding differentially private noise, and then generate synthetic data.

@@

To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information(MI) of the all database attribute pairs are calculated and then a maximum spanning tree(MST) algorithm was run with edge weights being the MIs to obtain a skeleton MST MRF.

@@

We came up with an alternative heuristic for a general purpose workflow. Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of this upper bounds.

For the measure step, we followed the examples provided in the tool's repository. Gaussian noises are added to the selected marginals. Half of the privacy budget are spent on all 1-way marginals and the other half on the selected cliques. These marginals are then fed to the tool to fit the MRF. By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.

>>>>

The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022}. We first select the important marginals to preserve, measure them by adding differentially private noise, and then generate synthetic data.

@@

To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information(MI) of all the database attribute pairs is calculated, and then a maximum spanning tree(MST) algorithm was run with edge weights being the MIs to obtain a skeleton MST MRF.

@@

We developed an alternative heuristic for a general-purpose workflow. Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of these upper bounds.

For the measure step, we followed the examples provided in the tool's repository. Gaussian noises are added to the selected marginals. Half of the privacy budget is spent on all 1-way marginals and the other half on the selected cliques. These marginals are then fed to the tool to fit the MRF. By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.
